Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-25 doc/main_jfm.tex
re-calculated table 1
conclusion draft

We calculate $\langle F\rangle$ by first evaluating the smooth tangential force along curves a positive distance inside and 
outside $\mathcal{C}_m$ respectively, and then interpolating at zero distance to give a force jump. 
We have made a slight abuse of language: due to the problem being two-dimensional,
the integral $\langle F\rangle$ is actually a force density per length which when divided by length gives the requisite force per area. 
which when divided by length

@@

>>>>

We calculate $\langle F\rangle$ by first evaluating the smooth tangential force along curves a positive distance inside and 
outside $\mathcal{C}_m$ respectively, and then interpolating at zero distance to give a force jump. 
We have made a slight abuse of language: due to the problem being two-dimensional,
the integral $\langle F\rangle$ is actually a force density per length which when divided by length gives the requisite force per area. 
%which when divided by length

@@

This study proposes a continuum coarse-grained model for Janus-vesicle that focuses on the 
hydrophobic interactions between lipids, and the hydrophobic force is derived and used for 
obtaining particle dynamics. The mobility problem using integral equation methods combining
the previously introduced HAPis adopted.
The imposed forces and torques of Janus particles adopt not only HAP but a newly developed short 
range repulsion given by \ref{eq:REPULforce} and \ref{eq:REPULtorque}.
The hydrodynamic stress tensor calculated in the algorithm leads to examinations of permeable 
membrane where the stretching modulus $K_A$ and the permeability constant $P$ can be obtained.
With the use of selected parameters, the numerical algorithm yields good qualitative results such as
phenomena in tank-treading Janus-vesicle, asymmetric slipper shape in a parabolic flow, and the membrane rupture in a flow at high shear rate.

Inter-monolayer friction coefficients are then obtained and reported by calculating the pressure jumps 
with respect to the bilayer midplane.
Results of two Janus-vesicles in flow simulations produce an outstanding agreement with ones generated 
using continuum modeling.

Our future goal is to extend the current framework to a three-dimensional Janus-vesicle system. 
The further implementation of adding a fast algorithms such as the fast multipole method is also a 
practical approach. Other physical properties of the bilayer membrane such as ......
